\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Meghan B. McGarry} % Your name
\address{414 N Sherman Ave \\ Madison WI 53704} % Your secondary addess (optional)
\address{(608)~332-9678 \\ mbmcgarry@wisc.edu} % Your phone number and email
\address{http://mbmcgarry.github.io} % Your address

\begin{document}

\noindent
\begin{rSection}{Education}
\begin{tabbing}
\indent 2008, 2010, 2011 \= Text \= \kill

\\
\bf{Ph.D.} \> {\bf University of Wisconsin - Madison}, Physics\\
2005 - 2013 \indent\> \emph{Probing the Relationship Between Magnetic and Temperature Structures} \\
\indent \> \emph{with Soft X-Rays on the Madison Symmetric Torus}\\
          \indent\> Advisor: Daniel J. Den Hartog\\
\\
\bf{B.A.} \> {\bf University of California, Berkeley}, Physics \& Astrophysics\\
1998 - 2002\\
\end{tabbing}
\end{rSection}

\noindent
\begin{rSection}{Technical Skills}
Computer Programming \hfill C++, IDL, Perl, Python \\
Databases \hfill MDSPlus, SQL \\
Languages \hfill English (native), Mandarin (intermediate), Spanish (proficient)\\
%Operating Systems \hfill Linux/Unix, Mac, Windows \\
Software \hfill \LaTeX, Microsoft Office Suite, Vectorworks \\
Version Control \hfill CVS, Git, GitHub \\
\end{rSection}

\noindent
\begin{rSection}{Honors and Awards}
\begin{tabbing}

\indent 2008, 2010, 2011 \= Text \= \kill
2014 - 2015 \> Consortium for Verification Technology Postdoctoral Fellowship \\

2008, 2010, 2011\> Hirschfelder Fellowship for Women in Physics, Mathematics, Chemistry \\

2004 \> Smithsonian Institution Special Achievement Award\\

2003 \> NASA Group Achievement Award - Chandra Mission Planning
and Review Subgroup \\

2001 \> NSF Research Experience for Undergraduates Fellowship \\

2000 \> Cal Space Summer Undergraduate Fellowship \\
  \end{tabbing}
\end{rSection}


\noindent
\begin{rSection}{Research Experience}
\begin{tabbing}
\indent 2008, 2010, 2011 \= Text \= \kill
%\indent Fillingspac \= Text \= \kill

2014 - Present \> {\bf University of Wisconsin - Madison}, Engineering Physics Dept.\\
\indent \> \emph{Assistant Scientist, Consortium for Verification Technology} \\
\indent \> \emph{Postdoctoral Researcher (2014 - 2015)} \\
\indent \> Using the Cyclus nuclear fuel cycle simulator to identify signatures of material diversion \\
\indent \> for proliferation. Developing heterogeneous synthetic datasets to develop anomaly \\
\indent \> detection algorithms.  \\
\\
2008 - 2014 \> {\bf University of Wisconsin - Madison}, Physics Dept.\\
\indent \> \emph{Postdoctoral Researcher (2013 - 2014), Madison Symmetric Torus} \\
\indent \> \emph{Graduate Research Assistant (2008 - 2013)} \\
\indent \> Quantified impact of impurities on soft x-ray (SXR) transmission of beryllium filters. \\
\indent \> Developed a double-filter SXR tomography diagnostic to study plasma temperature. \\
\\
\\
2006 - 2008 \> {\bf University of Wisconsin - Madison}, Engineering Physics Dept.\\
\indent \> \emph{Graduate Research Assistant, Pegasus} \\
\indent \> Designed SXR pinhole imaging camera to study magnetic structure. \\
\\
2002 - 2005 \> {\bf Harvard-Smithsonian Center for Astrophysics} \\
\indent \> \emph{Science Mission Planner, Chandra X-ray Observatory} \\
\indent \> Scheduled observations and wrote programs to maintain daily science operations. \\
\indent \> Studied observational properties of anomalous X-ray pulsars. \\
\\
2001      \> {\bf University of Hawaii at Manoa}, Institute for Astronomy \\
\indent \> \emph{Research Experience for Undergraduates} \\
\indent \> Used spectral modeling to determine galactic redshifts. \\
\\
2000      \> {\bf University of California, Berkeley}, Space Sciences Lab \\
\indent \> \emph{Cal Summer Science Undergraduate Fellow, SETI} \\
\indent \> Looked for optical extraterrestrial signals using coincidence-counting. \\
\end{tabbing}
\end{rSection}


\noindent
\begin{rSection}{Policy Experience}
\begin{tabbing}
\indent 2008, 2010, 2011 \= Text \= \kill
%\indent Fillingspac \= Text \= \kill
2015 \> {\bf 61st Pugwash Conference} \\
\indent \> \emph{Co-rapporteur - Nuclear Energy and Nonproliferation} \\
\indent \> Co-wrote the working group summary report on nuclear energy and non-proliferation. \\
\\
2014 \> {\bf Natural Resources Defense Council} \\
\indent \> \emph{Consultant - Energy Policy} \\
\indent \> Wrote a white paper analyzing recent progress at the National Ignition Facility. \\
\\
2009, 2011, 2013\> {\bf Union of Concerned Scientists}, Summer Symposium \\
\indent \> \emph{Participant - Global Security Policy} \\
\indent \> Presented original research on high-powered microwave anti-satellite weapons. \\
\\
2009\> {\bf U.S. Congress Fusion Day}, Washington, D.C. \\
\indent \> \emph{Participant} \\
\indent \> Met with representatives to discuss fusion research and US energy policy. \\
\end{tabbing}
\end{rSection}



\noindent
\begin{rSection}{Teaching Experience}
\begin{tabbing}
\indent 2008, 2010, 2011 \= Text \= \kill
%\indent Fillingspac \= Text \= \kill
%2015 \> {\bf American Nuclear Society Annual Summer Meeting}\\
%\indent \> \emph{Cyclus User and Archetype Developer Tutorial} \\
%\indent \> Workshops on how to run Cyclus fuel cycle simulator and design custom agents.
2005 - 2006 \> {\bf University of Wisconsin - Madison}, Physics Dept.\\
\indent \> \emph{Graduate Teaching Assistant - Introductory Physics} \\
\indent \> Taught discussion, laboratory and exam sessions for 100 students. \\
\end{tabbing}
\end{rSection}

\noindent
\begin{rSection}{Mentoring}
\begin{tabbing}
\indent 2008, 2010, 2011 \= Text \= \kill
%\indent Fillingspac \= Text \= \kill
~2016 - present \> Drew Buys, Masters Student (LaFollette School of Public Affairs) \\
~2015 - present \> Chris Hoffman, Masters Student (Nelson Institute-Environment and Resources) \\
~2014 \> Mike Gionet, Undergraduate (Engineering Physics) \\
~2012 \> Michelle Okoniewski, Masters Student (Engineering Physics) \\
~2011 - 2014 \> Jay Johnson, Undergraduate (Physics) \\
~2011 \> Zachary Billey, Ph.D. Student (Physics) \\
~2011 \> Jessica Rubio, Undergraduate (Engineering Physics) \\
\end{tabbing}
\end{rSection}

\newpage

\begin{rSection}{Service}
\begin{tabbing}
\indent 2008, 2010, 2011 \= Text \= \kill
%\indent Fillingspac \= Text \= \kill
~2015 \> Article Reviewer, \emph{Review of Scientific Instruments} \\
~2015 \> Engineering Career Panelist - Edgewood College, WI \\

~2015 \> Organized Local Screening for ``The Man Who Saved The World'', UW Madison \\

~2008 - 2009 \> Graduate Representative - Climate and Diversity Committee, UW Physics\\

~2008 - 2009 \> Co-Chair -Sea Kayaking Interest Group, Wisconsin Union Hoofers Outing Club \\

~2006 - 2007 \> Graduate Representative - Graduate Program Committee, UW Physics\\

~2004 - 2005 \> Mentor - 6th and 7th Grade, Cambridge Science Clubs for Girls Program \\

~2003 \> Mentor - NSF Research Experiences For Undergraduates,
    Harvard University\\
\end{tabbing}
\end{rSection}

\noindent
\begin{rSection}{Professional Development}
\begin{tabbing}
\indent 2008, 2010, 2011 \= Text \= \kill
%\indent Fillingspac \= Text \= \kill
~2015 \> American Nuclear Society Member \\
~2007 - 2013 \> American Physical Society (APS) Member \\
~2013 \> Union of Concerned Scientists Global Security Professional Meeting, Segni, Italy \\
~2008 \> APS Opportunities in Energy Research Workshop, New Orleans, Louisiana \\
~2003 \> NASA X-Ray Astronomy School, Wallops Island, Virginia \\
\end{tabbing}
\end{rSection}

\noindent
\begin{rSection}{Invited Talks}
\begin{tabbing}
\indent 2008, 2010, 2011 \= Text \= \kill
%\indent Fillingspac \= Text \= \kill
\emph{Modeling Material Diversion with the Cyclus Fuel Cycle Simulator} \\
Oct 2015\> International Student Young Pugwash Meeting \\
\> Nagasaki, Japan \\
Apr 2015\> Union of Concerned Scientists Global Security Webinar Series \\
\\
\emph{Defining the Threat of High-Powered Microwave Weapons in Space} \\
Jul 2011\> Union of Concerned Scientists Summer Symposium on Science and World Affairs \\ 
\> King's College, London, England \\
\\
\emph{High Powered Microwave Weapons - Political Fantasy or the Future of Space Warfare?} \\
Feb 2011 \> CISAC Research Seminar on International Security, Natural Science and \\
\> Social Science, Stanford University \\

Feb 2011 \> Science, Technology, Engineering and Policy Group Seminar, UC Berkeley \\

Jul 2009 \> Union of Concerned Scientists Summer Symposium on Science and World Affairs \\ 
\> Fudan University, Shanghai, China \\
\\
\emph{Soft X-ray Tomography on MST}\\
Oct 2009 \> Plasma Physics Seminar, Consorzio RFX, Padua, Italy \\
\end{tabbing}
\end{rSection}

\noindent
\begin{rSection}{Refereed Technical Publications}
J.J. Koliner, M.R. Cianciosa, J. Boguski, J.K. Anderson, J.D. Hanson, B.E. Chapman, D.L. Brower, D.J. Den Hartog, W.X. Ding, J.R. Duff, J.A. Goetz, {\bf M.B. McGarry}, L.A. Morton, E.B. Parke, ``3D Equilibrium Solutions for a Current-Carrying Reversed-Field Pinch Plasma with a Close-Fitting Conducting Shell'',  \emph{Phys. Plasmas}, {\bf 23}, 032508 (2016)

K.D. Huff, M.J. Gidden, R.W. Carlsen, R.R. Flanagan, {\bf M.B. McGarry}, A.C. Opotowsky, E.A. Schneider, A.M. Scopatz. P.P.H. Wilson, ``Fundamental Concepts in the Cyclus Fuel Cycle Simulator Framework'', \emph{Adv. Eng. Softw.}, {\bf 94}, 46 (2016)
\\
\\
M. Galante, L. Reusch, D.J. Den Hartog, P. Franz, J.Johnson, {\bf M.B. McGarry}, M. Nornberg, H. Stephens, ``Determination of $Z_{eff}$ by Integrating Measurements from X-ray tomography and Charge Exchange Recombination Spectroscopy'', \emph{Nuc. Fusion}, {\bf 55}, 123016 (2015)
\\
\\
J. Sarff, A. Almagri, J. Anderson, M. Borchardt, W. Capecchi, D. Carmody, K. Caspary, B. Chapman, D. Den Hartog, J. Duff, S. Eilerman, A. Falkowski, C. Forest, M. Galante, J. Goetz, D. Holly, J. Koliner, S. Kumar, J. Lee, D. Liu, K. McCollam, {\bf M. McGarry }, V. Mirnov, L. Morton, S. Munaretto, M. Nornberg, P. Nonn, S. Oliva, E. Parke, M. Pueschel, J. Reusch, J. Sauppe, A. Seltzman, C. Sovinec, D. Stone, D. Thuecks, M. Thomas, J. Triana, P. Terry, J. Waksman, G. Whelan, D. Brower, W. Ding, L. Lin, D. Demers, P. Fimognari, J. Titus, F. Auriemma, P. Franz, R. Lorenzini, E. Martines, B. Momo, P. Piovesan, M. Puiatti, M. Spolaore, D. Terranova, P. Zanca, V. Davydenko, A. Ivanov, S. Polosatkin, N. Stupishin, D. Spong, D. Craig, H. Stephens, R. Harvey, M. Cianciosa, J. Hanson, B. Breizman, M. Li, L. Zheng, ``Overview of Results from the MST Reversed Field Pinch Experiment'', \emph{Nuc. Fusion}, {\bf 55}, 104006 (2015)
\\
\\
{\bf M.B. McGarry}, P. Franz. D.J. Den Hartog, J.A. Goetz, ``Effect of Beryllium Filter Purity on X-ray Emission Measurements'', \emph{Plasma Phys. Contr. F.}, {\bf 56}, 125018 (2014)
\\
\\
{\bf M.B. McGarry}, P. Franz, D.J. Den Hartog, J.A. Goetz and J. Johnson, ``Note: Effect of Photodiode Aluminum Cathode Frame on Spectral Sensitivity in the Soft X-ray Energy Band'',  \emph{Rev. Sci. Instrum.}, {\bf 85}, 096105 (2014)
% canonical Te and ne profiles
\\
\\
L.M. Reusch, M.E. Galante, P. Franz, J.R. Johnson, {\bf M.B. McGarry}, H.D. Stephens, and D.J. Den Hartog, ``An integrated data analysis tool for improving measurements on the MST RFP'', \emph{Rev. Sci. Instrum.}, \textbf{85}, 11D844 (2014)
\\
\\
J.S. Sarff, A.F. Almagri, J.K. Anderson, M. Borchardt, D. Carmody, K. Caspary, B.E. Chapman, D.J. Den Hartog, J. Duff, S. Eilerman, A. Falkowski, C.B. Forest, J.A. Goetz, D.J. Holly, J-H. Kim, J. King, J. Ko, J. Koliner, S. Kumar, J.D. Lee, D. Liu, R. Magee, K.J. McCollam, {\bf M. McGarry}, V.V. Mirnov, M.D. Nornberg, P.D. Nonn, S.P. Oliva, E. Parke, J.A. Reusch, J.P. Sauppe, A. Seltzman, C.R. Sovinec, H. Stephens, D. Stone, D. Theucks, M. Thomas, J. Triana, P.W. Terry, J. Waksman, W.F. Bergerson, D.L. Brower, W.X. Ding, L. Lin, D.R. Demers, P. Fimognari, J. Titus, F. Auriemma, S. Cappello, P. Franz, P. Innocente, R. Lorenzini, E. Martines, B. Momo, P. Piovesan, M. Puiatti, M. Spolaore, D. Terranova, P. Zanca, V. Belykh, V.I. Davydenko, P. Deichuli, A.A. Ivanov, S. Polosatkin, N.V. Stupishin, D. Spong, D. Craig, R.W. Harvey, M. Cianciosa, J.D. Hanson, ``Overview of results from the MST reversed field pinch experiment'', \emph{Nucl. Fusion}, {\bf 53}, 104017 (2013)
\\
\\
\noindent
{\bf M.B. McGarry}, P. Franz, D. J. Den Hartog, J. A. Goetz, M. A. Thomas, M. Reyfman and S. T. A. Kumar, ``High-performance double-filter soft x-ray diagnostic for measurement of electron temperature structure and dynamics'', \emph{Rev. Sci. Instrum.}, \textbf{83}, 10E129 (2012)
\\
\\
{\bf M.B. McGarry}, P. Franz, D.J. den Hartog, J.A. Goetz, ``A New Double-Foil Soft x-ray Array to Measure Te on the MST Reversed Field Pinch", \emph{Rev. of Sci. Instrum.}, {\bf 81}, 10,10E516 (2010)
\\
\\
G.D. Garstka, E.A. Unterberg, D.J. Battaglia, M.W. Bongard, N.W. Eidietis, R.J. Fonck, M.J. Frost, {\bf M.B. McGarry}, A.C. Sontag, B.J. Squires, G.R. Winz
``Attainment of high normalized current by current profile manipulation in the pegasus toroidal experiment'', \emph{J. Fusion Energ.}, {\bf 27}, 20 (2008)
\\
\\
{\bf M.B. McGarry}, B.M. Gaensler, V.M. Kaspi, S.M. Ransom, S. Veljkovik, 
``X-Ray Timing, Spectroscopy, and Photometry of the Anomalous X-Ray Pulsar Candidate CXOU J010043.1-721134''
\emph{Astrophys. J. Lett.}, {\bf 627}, L137 (2005)
\\
\\
P.J. Green, J.D. Silverman, R.A. Cameron, D.-W. Kim, B.J Wilkes,
W.A. Barkhouse, A. LaCluyzé, D. Morris, A. Mossman, H. Ghosh,
J.P. Grimes, B.T. Jannuzi, H. Tananbaum, T.L. Aldcroft,
J.A. Baldwin, F.H. Chaffee, A. Dey, A. Dosaj, N.R. Evans,X. Fan,
C. Foltz, T. Gaetz, E.J. Hooper, V.L. Kashyap, S. Mathur, 
{\bf M.B. McGarry}, E. Romero-Colmenero, M.G. Smith, P.S. Smith, R.C. Smith,
G. Torres, A. Vikhlinin, D.R. Wik
`The Chandra Multi-wavelength Project: Optical Follow-up of
Serendipitous Chandra Sources''
\emph{Astrophys. J. Suppl. S.}, {\bf 150}, 1, 43 (2004) 
\\
\\
D. Werthimer, D. Anderson, C.S. Bowyer, J. Cobb,
 E. Heien, E.J Korpela, M.L. Lampton, M. Lebofsky,
  G.W. Marcy, {\bf M.B. McGarry}; D. Treffers
``Berkeley Radio and Optical SETI Program:SETI@home, SERENDIP, and
SEVENDIP'',
 \emph{SPIE Proceedings of the Third International Conference on Optical SETI}, {\bf 4273} (2001)
\\
\end{rSection}


% Eventually switch this section to Refereed Policy Pubs and 'Other Pubs'

\noindent
\begin{rSection}{Policy Publications}
{\bf M.B. McGarry}, ``Integrating Nuclear Science and Policy for a New Generation'', Web blog post, \emph{All Things Nuclear}, Union of Concerned Scientists, 18-Feb (2016) \\
http://allthingsnuclear.org/guest-commentary/integrating-nuclear-science-and-policy-for-a-new-generation
\\
\\
  C. Harrington \& {\bf M.B. McGarry} 
``Rapporteur's Report: Civilian Nuclear Energy, Energy Resources, and International Cooperation (Working Group 7)'',
\emph{61st Pugwash Conference on Science and World Affairs} (2015) \\
https://pugwashconferences.files.wordpress.com/2015/10/wg7-report.pdf 
\\
\\
{\bf M.B. McGarry} and L. Grego,
``High Powered Microwave Weapons in Space - Defining the Threat'' \\
\emph{Science and Global Security}, submitted Nov 18 (2015)
\\
\\
{\bf M.B. McGarry} \& P.P.H. Wilson
``Modeling Material Diversion with the Cyclus Nuclear Fuel Cycle Simulator,''
\emph{61st Pugwash Conference on Science and World Affairs}, available upon request (2015) \\
http://pugwash.org/2015/10/20/61st-pugwash-conference-nagasaki-1-5-november-2015/
\\
\\
{\bf M.B. McGarry} 
``The National Ignition Facility High-Foot Campaign: A New Approach to Ignition?''
\emph{Natural Resources Defense Council}, submitted June 16 (2014)
\\
\end{rSection}

\begin{rSection}{Other Publications}
\noindent
  {\bf M.B. McGarry}, 
``Probing the relationship between magnetic and temperature structures with soft x-rays on the Madison Symmetric Torus''
\emph{Ph.D. Dissertation - Physics}, University of Wisconsin-Madison (2013)
%\\
%\\
% Silicon Thickness Effects
%{\bf 2014}
%P. Franz, {\bf M. B. McGarry}, D. J. Den Hartog, and J. A. Goetz and J. Johnson, 41st EPS Conference on Plasma Physics Proceedings
\\
\end{rSection}

\noindent
\begin{rSection}{Conference Posters}
{\bf 2015}
``Survey of Cyclus Application for Non-proliferation'' \\
{\bf M.B. McGarry}, P.P.H Wilson, \\
\emph{Consortium for Verification Technology}, 2nd Annual Workshop, No. 4
\\
\\
{\bf 2015}
``Agent-Based Modeling of Open and Clandestine Fuel Cycle Facilities''\\
{\bf M.B. McGarry}, P.P.H Wilson, \\
\emph{University \& Industry Technical Interchange}, Consortium for Verification Technology

\newpage

{\bf 2013}
``SXR Double-Foil Measurements of Electron Temperature and Impurity Structures on MST''\\
{\bf M.B. McGarry}, P. Franz, D.J. den Hartog, J.A. Goetz, J. Johnson,  \\
\emph{American Physical Society, Division of Plasma Physics}, 55rd Annual Meeting, No.  CP8.00094 
\\
\\
{\bf 2011}
``Electron Temperature Measurement on MST Using SXR Brightness'' \\
{\bf M.B. McGarry}, P. Franz, D.J. den Hartog, J.A. Goetz, \\
 \emph{American Physical Society, Division of Plasma Physics}, 53rd Annual Meeting, No. BP9.00101
\\
\\
{\bf 2010}
``An Upgraded Soft X-Ray Tomography Diagnostic to Measure Electron Temperature on MST'' \\
{\bf M.B. McGarry}, P. Franz, J.A. Goetz, D.J. den Hartog, \\
 \emph{American Physical Society, Division of Plasma Physics}, 52nd Annual Meeting, No. PP9.061
\\
\\
{\bf 2009}
``Two-Color SXR Tomography on MST'' \\
{\bf M.B. McGarry}, J.A. Goetz, D.J. den Hartog, P. Franz  \\
\emph{American Physical Society, Division of Plasma Physics}, 51st Annual Meeting, No. TP8.053
\\
\\
{\bf 2008}
``Multicolor SXR Tomography on MST'' \\
{\bf M.B. McGarry}, J.A. Goetz, D.J. den Hartog, B.E. Chapman,
Franz, P., Bonomo, F., Marrelli, L.  \\
 \emph{American Physical Society, Division of Plasma Physics}, 50th Annual Meeting, No. NP6.050
\\
\\
{\bf 2007}
``An Upgraded Soft X-ray Pinhole Camera for Current Profile Measurements on the Pegasus Toroidal Experiment'' \\
{\bf M.B. McGarry}, M.J. Frost, G.R. Winz, A.C. Sontag, \\
\emph{American Physical Society, Division of Plasma Physics}, 49th Annual Meeting, No. TP8.113
\\
\\
{\bf 2004}
``A Closer Look at a Possible New Anomalous X-Ray Pulsar'' \\
{\bf M.B. McGarry}, B.M. Gaensler, S. Veljkovik, V.M. Kaspi, S.M. Ransom,  \\
 \emph{American Astronomical Society}, Meeting 204, No. 74.11
\\
\\
{\bf 2003} 
``Simulating the Origin and Evolution of Accreting Millisecond X-Ray Pulsars''\\
{\bf M.B. McGarry}, J.S. Heyl\\
\emph{American Astronomical Society}, Meeting 203, No. 53.10
\\ 
\end{rSection}

%\newpage

\end{document}

